#Name: Vaishali Mali
##Task 2: To predict a score of a student if he studies for 9.25 hours in a day by supervised machine learning.
###Simple Linear Regression Model.
** Input Data as x as no of hours of study and y as scores obtained**
```{r}
x=c(2.5,5.1,3.2,8.5,3.5,1.5,9.2,5.5,8.3,2.7,7.7,5.9,4.5,3.3,1.1,8.9,2.5,1.9,6.1,7.4,2.7,4.8,3.8,6.9,7.8)
y=c(21,47,27,75,30,20,88,60,81,25,85,62,41,42,17,95,30,24,67,69,30,54,35,76,86)
n=25
p=2
```
** To study the relation between x and y through scatter diagram **
```{r}
plot(x,y,pch=18,xlab = "Study Hours",ylab="Scores Obtained",main = "Scatter Diagram")
r=cor(x,y)
r               #since |r|> 0.8 there is a strong positive correlation in between x and y
cor.test(x,y,method="pearson",alt="two.sided")
2*pt(3.818,8,lower.tail = F)   # To get a P-value
```
**Fitting a Model to the given data**
```{r}
fit=lm(y~x)
fit
B0_hat=2.483673
B1_hat=9.775803
y_hat=B0_hat+B1_hat*x   #fitted simple linear regression 
summary(fit) 
glm(y~x,family = gaussian)
aov(fit)
```
**Percentage of exlained variation**
```{r}
14624.172/(14624.172+722.068)*100
#The model explains 95.29482 % of the variability in the dependent variable by the independent variable
```
**Residual plots**
```{r}
res=(y-y_hat)
qqnorm(res)
par(mfrow=c(2,2))
plot(fit)
fit$fitted
fit$residuals
fit$coefficient
e1=fit$fitted.values
shapiro.test(e1)
```
**Predicted Score when x=9.25**
```{r}
y_est=2.483673+9.775803*9.25  
y_est 
```
**Conclusion:**
`If a student studies for 9.25 hours in a day then he should get 92.90985 percentage of marks.`

                                           --Thank You--









